\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}

### 2025-01-17 paper/main.tex
updated Table 1 caption, tikz figure caption; added footnote about # LoRAs per layer

We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
Our central question is how \emph{total} verification, proof generation, and settings times grow with \textbf{the number of LoRA modules} (\#LoRA), while also considering each LoRA's average parameter size. 
Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.

@@

\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
Base Model & \# of LoRAs & Avg LoRA Params & Avg Settings & Avg Proof \\
\hline
distilgpt2 & 24 & 24576 & 38.0 & 31.6 \\
openai-community/gpt2 & 48 & 49152 & 43.6 & 34.9 \\
meta-llama/Llama-3.2-1B & 32 & 26624 & 37.2 & 31.0 \\
meta-llama/Llama-3.3-70B-Instruct & 80 & 147456 & 54.9 & 46.9 \\
meta-llama/Llama-3.1-8B-Instruct & 32 & 163840 & 57.4 & 47.7 \\
mistralai/Mixtral-8x7B-Instruct-v0.1 & 32 & 327680 & 86.1 & 73.7 \\
\hline
\end{tabular}
\caption{Model Performance Metrics}\label{tab:settings_proof}
\end{table}

@@

Table~\ref{tab:settings_proof} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size). These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships. The \emph{Base Model User}, meanwhile, benefits from the relatively short verification overhead.

@@

\end{tikzpicture}
\caption{Flow in a Multi-Party Inference scenario between local base model and remote LoRA weights. 
The base model performs a local forward pass, computing \(\mathbf{base\_out} = \mathbf{Wx}\). In parallel, the input \(\mathbf{x}\) is sent to the remote LoRA module, which returns \(\mathbf{\Delta} = \mathbf{BAx}\). The final output is \(\mathbf{base\_out} + \mathbf{\Delta}\).}
\label{fig:remote-lora-flow}
\end{figure}

>>>>

We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size. 
Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off. \footnote{Note that the number of LoRA modules in a given model is not purely a function of number of layers -- it is also a choice of which weight matrices within each layer is targeted. For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer, but, for example targeting the Query, Key, and Value matrices yeild three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}

@@

\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
Base Model & \# of LoRAs & Avg LoRA Size & Avg Settings & Avg Proof \\
\hline
distilgpt2 & 24 & 24576 & 38.0 & 31.6 \\
openai-community/gpt2 & 48 & 49152 & 43.6 & 34.9 \\
meta-llama/Llama-3.2-1B & 32 & 26624 & 37.2 & 31.0 \\
meta-llama/Llama-3.3-70B-Instruct & 80 & 147456 & 54.9 & 46.9 \\
meta-llama/Llama-3.1-8B-Instruct & 32 & 163840 & 57.4 & 47.7 \\
mistralai/Mixtral-8x7B-Instruct-v0.1 & 32 & 327680 & 86.1 & 73.7 \\
\hline
\end{tabular}
\caption{Model benchmark results for Settings and Proof generation time averaged by number of LoRA modules.}\label{tab:settings_proof}
\end{table}

@@

Table~\ref{tab:settings_proof} similarly shows that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size). These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships. The \emph{Base Model User}, meanwhile, benefits from the relatively short verification overhead.

@@

\end{tikzpicture}
\caption{Flow in a Multi-Party Inference scenario between local base model and remote LoRA weights. 
The base model performs a local forward pass, computing \(\mathbf{base\_out} = \mathbf{Wx}\). In parallel, the input \(\mathbf{x}\) is sent to the remote LoRA module, which returns \(\mathbf{\Delta} = \mathbf{BAx}\), where \(\mathbf{B,A}\) are the low-rank finetuned matrices. The final output is \(\mathbf{base\_out} + \mathbf{\Delta}\).}
\label{fig:remote-lora-flow}
\end{figure}
